---
title: Data Analysis including 2020 and 2021 Season."Development of criteria for variable
  N-fertilizer and irrigation management of potatoes"
author: "Fernando Bortolozo"
date: "10/29/2021"
output:
  html_document: 
    toc: yes
    fig_caption: yes
  word_document: default
  pdf_document: default
---


```{r, package_options, echo=FALSE, warning=FALSE, message=FALSE}
library(readxl)
library(dplyr)
library(ggplot2)
library(ExpDes)
library(tidyverse)
library(vtable)
library(esquisse)
library(dslabs)
library(Hmisc)
library(agricolae)
library(agridat)
library(devtools)
library(ggfortify)
library(MASS)
library(car)
library(RCurl)
library(skimr)
library(gtsummary)
library(cowplot)
library(ggstatsplot)
library(hrbrthemes)
library(table1)
library(arsenal)
library(ggstatsplot)
library(multcompView)
library(egg) 
library(datasets)
```

# 1. Exploratory Analisys
Total yield distribution across sites,irrigation methods and season for In-season decision, Grower's practice and UF/IFAS N-fertilizer application. The total yield response was 28687.47, 29676.20, and 29411.81 lbs./acre for fixed N application rate, grower's practice, and in-season decision N application respectively. There is no significant statistical difference between treatments. This results did not specify factor such as site, irrigation and year. 

## **1.1 Summary**
```{r, echo=FALSE}
Alldata <- read_excel("~/Off-site N trial/Alldata.xlsx")
dados<-(Alldata)
#describe(dados)
#par(mfrow=c(2,2))
#truehist(dados$tyield)
#truehist(log(dados$tyield))
#qqPlot(dados$tyield)
#title("Normal QQ-plot")
#qqPlot(log(dados$tyield))
#title("Normal QQ-plot")
#plot.graph.freq(dados$tyield)

summary(dados)
shapiro.test(dados$tyield)

```




# 1.2. Total yield for Sseepage (SEP) and Subirrigation Drain Tile (SDT) 

#### **Figure 1.**Total Yield Response considering N rates Fertilizer for Arlie and Parker accounting 2020 and 2021 Season for Seepage (SEP) Irr. System.
```{r, echo=FALSE}
Alldata %>%
  filter(irrig %in% "SEEP") %>%
  ggplot() +
  aes(x = Trt_, y = tyield, fill = farm) +
  geom_boxplot(shape = "circle") +
  scale_fill_hue(direction = 1) +
  coord_cartesian(ylim=c(10000, 50000)) + 
  scale_y_continuous(breaks = seq (10000, 50000, 5000))+
  labs(
    x = "Treatments ",
    y = "Yield (lbs./acre)",
    title = "Seepage Yield data 2020 and 2021",
    fill = "Farm ID"
  ) +
  theme_bw() +
  theme(
    plot.title = element_text(face = "bold",
                              hjust = 0.5),
    axis.title.y = element_text(size = 12L,
                                face = "bold"),
    axis.title.x = element_text(size = 12L,
                                face = "bold")
  ) +
  facet_grid(vars(), vars(year))

# Esquisse Plot TILE- Arlie and Parker 2020-2021

Alldata %>%
  filter(irrig %in% "TILE") %>%
  ggplot() +
  aes(x = Trt_, y = tyield, fill = farm) +
  geom_boxplot(shape = "circle") +
  scale_fill_hue(direction = 1) +
  coord_cartesian(ylim=c(1000, 50000)) + 
  scale_y_continuous(breaks = seq (1000, 50000, 5000))+
  labs(
    x = "Treatments ",
    y = "Yield (lbs./acre)",
    title = "Tile yield data 2020 and 2021",
    fill = "Farm ID"
  ) +
  theme_bw() +
  theme(
    plot.title = element_text(face = "bold",
                              hjust = 0.5),
    axis.title.y = element_text(size = 12L,
                                face = "bold"),
    axis.title.x = element_text(size = 12L,
                                face = "bold")
  ) +
  facet_grid(vars(), vars(year))

```




### **Anova and TukeyHSD test** 
#### **Figure 2.** Total Yield distribution Across Farms, Irr. Systems, and Year for Each Treatment
```{r, echo=FALSE}
ggbetweenstats(
  data = dados,
  x = Trt,
  y = tyield,
  title = " ",
  xlab = "Treatments",
  ylab = "Total yield (lbs./acre)",
)

#> t is large; approximation invoked.

```





### **Pairwise test** 
#### **Figure 2.** Total Yield distribution Across Farms, Irr. Systems, and Year for Each Treatment

```{r, echo=FALSE}
Alldata <- read_excel("~/Off-site N trial/Alldata.xlsx")
dados<-(Alldata)
#str (dados)
#any(is.na())
#head(dados)

anova <- aov(tyield ~Trt, data = dados)
summary(anova)

tukey <- TukeyHSD(anova)
print(tukey)

cld <- multcompLetters4(anova, tukey)
print(cld)

Tk <- group_by (dados, Trt) %>%
      summarise(mean=mean(tyield), quant = quantile(tyield, probs = 0.75)) %>%
      arrange(desc(mean))

cld <- as.data.frame.list(cld$Trt)
Tk$cld <- cld$Letters
print(Tk)

ggplot(dados, aes(Trt, tyield)) + 
  geom_boxplot(aes(fill = factor(..middle..)), show.legend = FALSE) +
  labs(x="Treatments", y=" Total Yield (lbs/acre)") +
  theme_bw() + 
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank()) +
  geom_text(data = Tk, aes(x = Trt, y = quant, label = cld), size = 5, vjust=-1, hjust =-1) +
  scale_fill_brewer(palette = "Blues")
                
ggsave("boxplot.png", width = 4, height = 6, dpi = 1000)



```





```{r eval=FALSE, include=FALSE}
str(chickwts)

# analysis of variance
anova <- aov(weight ~ feed, data = chickwts)
summary(anova)

# Tukey's test
tukey <- TukeyHSD(anova)
print(tukey)

# compact letter display
cld <- multcompLetters4(anova, tukey)
print(cld)

# table with factors and 3rd quantile
Tk <- group_by(chickwts, feed) %>%
  summarise(mean=mean(weight), quant = quantile(weight, probs = 0.75)) %>%
  arrange(desc(mean))

# extracting the compact letter display and adding to the Tk table
cld <- as.data.frame.list(cld$feed)
Tk$cld <- cld$Letters

print(Tk)

# boxplot
ggplot(chickwts, aes(feed, weight)) + 
    geom_boxplot()
# boxplot
ggplot(chickwts, aes(feed, weight)) + 
  geom_boxplot() +
  labs(x="Feed Type", y="Weight (g)")
# boxplot
ggplot(chickwts, aes(feed, weight)) + 
  geom_boxplot() +
  labs(x="Feed Type", y="Weight (g)") +
  theme_bw() + 
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank())
# boxplot
ggplot(chickwts, aes(feed, weight)) + 
  geom_boxplot() +
  labs(x="Feed Type", y="Weight (g)") +
  theme_bw() + 
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank()) +
  geom_text(data = Tk, aes(x = feed, y = quant, label = cld))

# boxplot
ggplot(chickwts, aes(feed, weight)) + 
  geom_boxplot() +
  labs(x="Feed Type", y="Weight (g)") +
  theme_bw() + 
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank()) +
  geom_text(data = Tk, aes(x = feed, y = quant, label = cld), size = 3, vjust=-1, hjust =-1)

# boxplot
ggplot(chickwts, aes(feed, weight)) + 
  geom_boxplot(fill = "lightblue", color = "darkblue") +
  labs(x="Feed Type", y="Weight (g)") +
  theme_bw() + 
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank()) +
  geom_text(data = Tk, aes(x = feed, y = quant, label = cld), size = 3, vjust=-1, hjust =-1, color = "darkblue")


# boxplot
ggplot(chickwts, aes(feed, weight)) + 
  geom_boxplot(aes(fill = feed)) +
  labs(x="Feed Type", y="Weight (g)") +
  theme_bw() + 
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank()) +
  geom_text(data = Tk, aes(x = feed, y = quant, label = cld), size = 3, vjust=-1, hjust =-1)


# boxplot
ggplot(chickwts, aes(feed, weight)) + 
  geom_boxplot(aes(fill = feed), show.legend = FALSE) +
  labs(x="Feed Type", y="Weight (g)") +
  theme_bw() + 
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank()) +
  geom_text(data = Tk, aes(x = feed, y = quant, label = cld), size = 3, vjust=-1, hjust =-1) +
  scale_fill_brewer(palette = "Pastel1")


# boxplot
ggplot(chickwts, aes(feed, weight)) + 
  geom_boxplot(aes(fill = factor(..middle..)), show.legend = FALSE) +
  labs(x="AAAAA", y="Weight (g)") +
  theme_bw() + 
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank()) +
  geom_text(data = Tk, aes(x = feed, y = quant, label = cld), size = 6, vjust=-1, hjust =-1) +
  scale_fill_brewer(palette = "Blues")

```


 3. Total yield
 
#### **Figure 3.**Total Yield Response considering N rates Fertilizer for Arlie and Parker accounting 2020 and 2021 Season for Tile (SDT) Irr. System.


# Total Yield Response for N rates for SEP on Parker at 2020

```{r, echo=FALSE}
#Parker SEP (2020)
Parker1a <- filter(dados, year =="2020", irrig =="SEEP", farm =="Parker")
#str(Parker1a)
#View(Parker1a)
#class(Parker1a)
rbd(Parker1a$Trt_,Parker1a$block,Parker1a$tyield,quali = TRUE, nl = FALSE,hvar = "oneillmathews",sigT = 0.05,sigF = 0.05,unfold = NULL)
#set option for browser 
options("esquisse.display.mode" ="browser")
#set option for Rstudio dialog window
options("esquisse.display.mode" = "dialog")

#Esquisse plot 
Parker1a %>%
  filter(irrig %in% "SEEP") %>%
  ggplot() +
  aes(x = Trt, y = tyield, fill = farm) +
  geom_boxplot(shape = "circle") +
  scale_fill_hue(direction = 1) +
  coord_cartesian(ylim=c(1000, 50000)) + 
  scale_y_continuous(breaks = seq (1000, 50000, 5000))+
  labs(
    x = "Treatments ",
    y = "Yield (lbs./acre)",
    title = "Total Yield Across N rates for SEP on Parker at 2020",
    fill = "Farm ID"
  ) +
  theme_bw() +
  theme(
    plot.title = element_text(face = "bold",
                              hjust = 0.5),
    axis.title.y = element_text(size = 12L,
                                face = "bold"),
    axis.title.x = element_text(size = 12L,
                                face = "bold")
  ) +
  facet_grid(vars(), vars(year))

ggbetweenstats(
  data = Parker1a,
  x = Trt_,
  y = tyield,
  title = "Distribution of Total Yield Across N rates for SEP on Parker at 2020"
)





```


# Total Yield Response for N rates for SEP on Parker at 2021

```{r, echo=FALSE}
#Parker SEP (2021)
Parker1b <- filter(dados, year =="2021", irrig =="SEEP", farm =="Parker")
#str(Parker1b)
#View(Parker1b)
#class(Parker1b)
rbd(Parker1b$Trt_,Parker1b$block,Parker1b$tyield,quali = TRUE, nl = FALSE,hvar = "oneillmathews",sigT = 0.05,sigF = 0.05,unfold = NULL)

# plot
Parker1b %>%
  filter(irrig %in% "SEEP") %>%
  ggplot() +
  aes(x = Trt, y = tyield, fill = farm) +
  geom_boxplot(shape = "circle") +
  scale_fill_hue(direction = 1) +
  coord_cartesian(ylim=c(1000, 50000)) + 
  scale_y_continuous(breaks = seq (1000, 50000, 5000))+
  labs(
    x = "Treatments ",
    y = "Yield (lbs./acre)",
    title = "Total Yield Across N rates for SEP on Parker at 2021",
    fill = "Farm ID"
  ) +
  theme_bw() +
  theme(
    plot.title = element_text(face = "bold",
                              hjust = 0.5),
    axis.title.y = element_text(size = 12L,
                                face = "bold"),
    axis.title.x = element_text(size = 12L,
                                face = "bold")
  ) +
  facet_grid(vars(), vars(year))
            
# plot
ggbetweenstats(
  data = Parker1b,
  x = Trt_,
  y = tyield,
  title = "Distribution of Total Yield Across N rates for SEP on Parker at 2020"
)
```


# Total Yield Response for N rates for SEP on Smith at 2020

```{r, echo=FALSE}
Alldata <- read_excel("~/Off-site N trial/Alldata.xlsx")
view(Alldata)
dadosm<-(Alldata)
str(dadosm)
Smith1a <- filter(dadosm, year =="2020", irrig =="SEEP", farm =="Arlie")
#dados1a
#str(dados1a)
#View(dados1a)
#class(dados1a)
rbd(Smith1a$Trt_,Smith1a$block,Smith1a$tyield,quali = TRUE, nl = FALSE,hvar = "oneillmathews",sigT = 0.05,sigF = 0.05,unfold = NULL)


#plot
Smith1a %>%
  filter(irrig %in% "SEEP") %>%
  ggplot() +
  aes(x = Trt_, y = tyield, fill = farm) +
  geom_boxplot(shape = "circle") +
  scale_fill_hue(direction = 1) +
  coord_cartesian(ylim=c(1000, 50000)) + 
  scale_y_continuous(breaks = seq (1000, 50000, 5000))+
  labs(
    x = "Treatments ",
    y = "Yield (lbs./acre)",
    title = "Total Yield Across N rates for SEP on Smith at 2020",
    fill = "Farm ID"
  ) +
  theme_bw() +
  theme(
    plot.title = element_text(face = "bold",
                              hjust = 0.5),
    axis.title.y = element_text(size = 12L,
                                face = "bold"),
    axis.title.x = element_text(size = 12L,
                                face = "bold")
  ) +
  facet_grid(vars(), vars(year))
            
# plot
ggbetweenstats(
  data = Smith1a,
  x = Trt_,
  y = tyield,
  title = "Distribution of Total Yield Across N rates for SEP on Parker at 2020"
)
```

# Total Yield Response for N rates for SEP on Smith at 2021


```{r, echo=FALSE}
Alldata <- read_excel("~/Off-site N trial/Alldata.xlsx")
#view(Alldata)
dadosm<-(Alldata)
#str(dadosm)
Smith1b <- filter(dadosm, year =="2020", irrig =="SEEP", farm =="Arlie")
#dados1a
#str(dados1a)
#View(dados1a)
#class(dados1a)
rbd(Smith1a$Trt_,Smith1a$block,Smith1a$tyield,quali = TRUE, nl = FALSE,hvar = "oneillmathews",sigT = 0.05,sigF = 0.05,unfold = NULL)


#plot
Smith1a %>%
  filter(irrig %in% "SEEP") %>%
  ggplot() +
  aes(x = Trt_, y = tyield, fill = farm) +
  geom_boxplot(shape = "circle") +
  scale_fill_hue(direction = 1) +
  coord_cartesian(ylim=c(1000, 50000)) + 
  scale_y_continuous(breaks = seq (1000, 50000, 5000))+
  labs(
    x = "Treatments ",
    y = "Yield (lbs./acre)",
    title = "Total Yield Across N rates for SEP on Smith at 2021",
    fill = "Farm ID"
  ) +
  theme_bw() +
  theme(
    plot.title = element_text(face = "bold",
                              hjust = 0.5),
    axis.title.y = element_text(size = 12L,
                                face = "bold"),
    axis.title.x = element_text(size = 12L,
                                face = "bold")
  ) +
  facet_grid(vars(), vars(year))
            
# plot
ggbetweenstats(
  data = Smith1a,
  x = Trt_,
  y = tyield,
  title = "Distribution of Total Yield Across N rates for SEP on Smith at 2021"
)


```

